% Curriculum vitae

% Amanda Regan | aeregan@clemson.edu | http://amanda-regan.com

\documentclass[11pt]{article}
\usepackage{microtype}
\frenchspacing
\usepackage[letterpaper,margin=1in]{geometry}
\setlength\parindent{0in}
\setlength\parskip{6pt}
\setlength{\emergencystretch}{3em}
\usepackage[osf,sc]{mathpazo}

% headers and footers
\usepackage{fancyhdr}
\pagestyle{plain}
\frenchspacing

% Font
\usepackage{XCharter}

% HEADINGS
\usepackage{sectsty}
\usepackage{titlesec}
\usepackage[normalem]{ulem}
\sectionfont{\rmfamily\mdseries\Large}
\subsubsectionfont{\rmfamily\mdseries\bfseries\scshape\normalsize}
\subsectionfont{\rmfamily\bfseries\upshape\normalsize}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsubsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
% disables chapter, section and subsection numbering
\setcounter{secnumdepth}{-1}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% PDF SETUP
\PassOptionsToPackage{hyphens}{url}\usepackage[hidelinks, breaklinks, pdftex, pdftitle={Amanda E. Regan - CV}, pdfauthor={Amanda E. Regan}]{hyperref}

% DOCUMENT
\begin{document}
\thispagestyle{fancy}
\fancyfoot{}
\fancyhead{}
\renewcommand{\headrulewidth}{0pt}

%%% The next line will put the date revised in footer of first page
\rfoot{\scriptsize Current as of \today}

\hfill\hfill\hfill
\hfill\hfill\hfill
\hfill\hfill\hfill
\hfill\hfill\hfill
\begin{minipage}[t]{1.6in}
  \flushleft{\scriptsize  \texttt{\href{mailto:aeregan@clemson.edu}{aeregan@clemson.edu}}} \\
  \vspace{-0.065in}{\scriptsize  \url{https://amanda-regan.com}} \\
  \vspace{-0.065in}{\scriptsize  ORCID:
  \href{https://orcid.org/0000-0002-4260-5839}{\texttt{0000-0002-4260-5839}}}
\end{minipage}
\hfill
\begin{minipage}[t]{1.9in}
  \flushleft{{\scriptsize {Department of History and Geography} \\ Clemson University \\ 126D Hardin Hall \\ \vspace{-0.05in}
      Clemson, SC 29634}}
\end{minipage}


\vspace{0.1in}

{\Large\bfseries Amanda E. Regan}

\subsection{Appointments}\label{current-position}

Assistant Professor, Department of History and Geography, Clemson Univeristy, (2022 - present)

Lecturer, Department of History and Geography, Clemson University, (2021 - 2022)

Digital Humanities Postdoctoral Fellow, Center for Presidential History, Southern Methodist University, (2019 - 2021).

\subsection{Education}\label{education}
PhD history, George Mason University (2019)

MA history, California State University, San Marcos (2013)

BA history, California State University, San Marcos (2011)

\subsection{Books}
\emph{Shaping Up: Physical Fitness Initiatives for Women, 1880-1965}, (Under contract, University of Virginia Press).

\subsection{Peer Reviewed Journal Articles and Book Chapters}\label{peer-reviewed}
``Secret Societies and Revolving Doors: Using Mapping the Gay Guides to Study LGBTQ Life in the United States, 1965-1989,'' \emph{Journal of Digital History} 3, no. 1, (2024) \url{https://journalofdigitalhistory.org/en/article/X3MGSKqAycaT?idx=1&layer=narrative}

Amanda Regan, Laura Crossley, and Josh Catalano, ``Grant Funded Research and Graduate Student Success,'' in \emph{Digital Futures of Graduate Study in the Humanities}, ed. Anouk Lang, Gabriel Hankins and Simon Appleford. University of Minnesota Press, 2024.

Amanda Regan and Eric Gonzaba, ``Mapping the `New Gay South:' Queer Space and Southern Life 1965-1980,'' \emph{The Southern Quarterly} 58, no. 1, (2020): 11-25. \url{muse.jhu.edu/article/868177}.

``Mining Mind and Body: Approaches and Considerations for Using Topic Modeling to Identify Discourses in Digitized Publications,'' \emph{Journal of Sport History} 44, no. 2 (Summer 2017):160-77. \url{https://doi.org/10.5406/jsporthistory.44.2.0160}

\subsection{Digital History Projects}

Amanda Regan, Cameron Blevins, Eric Gonzaba, and Annelise Heinz, ``Queer Cartographies: Mapping Diverging and Overlapping Spaces in Gaia's Guide and Bob Damron's Address Book, 1970-1990,'' (in progress 2022-).

Amanda Regan and Eric Gonzaba, \emph{Mapping the Gay Guides}, (in progress 2019-): \url{http://www.mappingthegayguides.org}.

Joshua Catalano and Amanda Regan, ``Mining Eleanor Roosevelt's \emph{My Day} Columns,'' (2017) \url{https://regan008.shinyapps.io/mining_my_day/}.

Jannelle Legg, Amanda Regan, and Anne Ladyem McDivitt, \emph{Roy Rosenzweig Center for History and New Media 20th Anniversary Archive}, (2014). \url{http://20.rrchnm.org/}.


\subsection{Grants and Fellowships}
PI, ``Shaping Up: Physical Fitness Initiatives for Women, 1880-1965.'' Faculty Research Development Program grant from the College of Architecture, Arts and Humanities, Clemson University (2023-2024): \$2,500.

Co-Project Director, ``Mapping the Gay Guides: Understanding Historical LGBTQ Spaces through Gay Travel Guides.'' Humanities Collections and Reference Resources grant from the National Endowment for the Humanities (2021-2024): \$349,894.

Co-Primary Investigator, \emph{Mapping the Gay Guides.} Research, Scholarship, and Creative Activities Incentive grant from California State University, Fullerton (2019-2020): \$14,715.

\subsection{Awards and Honors}
Honorable Mention, Garfinkel Prize in Digital Humanities for \emph{Mapping the Gay Guides}, 2020, Digital Humanities Caucus of the American Studies Association.

Emerging Open Scholarship Award for \emph{Mapping the Gay Guides}, 2021, Canadian Social Knowledge Institute.

Louise and Rudolf Fishel Graduate Fellowship, 2018, George Mason University, Fairfax, VA.

Joseph and Dorothy Censer Fellowship, 2016, George Mason University, Fairfax, VA.

Larry J. Hackman Research Residency, 2016, New York State Archives, Albany, NY.

Provost's Dissertation Completion Travel Grant, 2016, George Mason University, Fairfax, VA.

Passed Ph.D. Oral Comprehensive Exams with Distinction, George Mason University, Fairfax, VA.

Digital History Fellowship, 2013-2015, Roy Rosenzweig Center for History and New Media, George Mason University, Fairfax, VA.

Digital Humanities Summer Institute Tuition Scholarship 2014, 2015, University of Victoria, Victoria, B.C.

Distinguished Master's Thesis Award, 2013, California State University, San Marcos, Department of History, San Marcos CA.

\end{document}