% Curriculum vitae

% Amanda Regan | aeregan@clemson.edu | http://amanda-regan.com

\documentclass[11pt]{article}
\usepackage{microtype}
\frenchspacing
\usepackage[letterpaper,margin=1in]{geometry}
\setlength\parindent{0in}
\setlength\parskip{6pt}
\setlength{\emergencystretch}{3em}
\usepackage[osf,sc]{mathpazo}

% headers and footers
\usepackage{fancyhdr}
\pagestyle{plain}
\frenchspacing

% Font
\usepackage{XCharter}

% HEADINGS
\usepackage{sectsty}
\usepackage{titlesec}
\usepackage[normalem]{ulem}
\sectionfont{\rmfamily\mdseries\Large}
\subsubsectionfont{\rmfamily\mdseries\bfseries\scshape\normalsize}
\subsectionfont{\rmfamily\bfseries\upshape\normalsize}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsubsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
% disables chapter, section and subsection numbering
\setcounter{secnumdepth}{-1}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% PDF SETUP
\PassOptionsToPackage{hyphens}{url}\usepackage[hidelinks, breaklinks, pdftex, pdftitle={Amanda E. Regan - CV}, pdfauthor={Amanda E. Regan}]{hyperref}

% DOCUMENT
\begin{document}
\thispagestyle{fancy}
\fancyfoot{}
\fancyhead{}
\renewcommand{\headrulewidth}{0pt}

%%% The next line will put the date revised in footer of first page
\rfoot{\scriptsize Current as of \today}

\hfill\hfill\hfill
\hfill\hfill\hfill
\hfill\hfill\hfill
\hfill\hfill\hfill
\begin{minipage}[t]{1.6in}
  \flushleft{\scriptsize  \texttt{\href{mailto:aeregan@clemson.edu}{aeregan@clemson.edu}}} \\
  \vspace{-0.065in}{\scriptsize  \url{https://amanda-regan.com}} \\
  \vspace{-0.065in}{\scriptsize  ORCID:
  \href{https://orcid.org/0000-0002-4260-5839}{\texttt{0000-0002-4260-5839}}}
\end{minipage}
\hfill
\begin{minipage}[t]{1.9in}
  \flushleft{{\scriptsize {Department of History and Geography} \\ Clemson University \\ 126D Hardin Hall \\ \vspace{-0.05in}
      Clemson, SC 29634}}
\end{minipage}


\vspace{0.1in}

{\Large\bfseries Amanda E. Regan}

\subsection{Appointments}\label{current-position}

Assistant Professor, Department of History and Geography, Clemson Univeristy, (2022 - present)

Lecturer, Department of History and Geography, Clemson University, (2021 - 2022)

Digital Humanities Postdoctoral Fellow, Center for Presidential History, Southern Methodist University, (2019 - 2021).

\subsection{Education}\label{education}
PhD history, George Mason University (2019)

MA history, California State University, San Marcos (2013)

BA history, California State University, San Marcos (2011)


\subsection{Peer Reviewed Publications}\label{peer-reviewed}

\emph{Shaping Up: Physical Fitness Initiatives for Women, 1880-1965}, (Under contract, University of Virginia Press).

``Secret Societies and Revolving Doors: Using Mapping the Gay Guides to Study LGBTQ Life in the United States, 1965-1989,'' \emph{Journal of Digital History} 3, no. 1, (2024) \url{https://journalofdigitalhistory.org/en/article/X3MGSKqAycaT?idx=1&layer=narrative}

Amanda Regan, Laura Crossley, and Josh Catalano, ``Grant Funded Research and Graduate Student Success,'' in \emph{Digital Futures of Graduate Study in the Humanities}, ed. Anouk Lang, Gabriel Hankins and Simon Appleford. (Forthcoming, University of Minnesota Press, December 2024).

Amanda Regan and Eric Gonzaba, ``Mapping the `New Gay South:' Queer Space and Southern Life 1965-1980,'' \emph{The Southern Quarterly} 58, no. 1, (2020): 11-25. \url{muse.jhu.edu/article/868177}.

``Mining Mind and Body: Approaches and Considerations for Using Topic Modeling to Identify Discourses in Digitized Publications,'' \emph{Journal of Sport History} 44, no. 2 (Summer 2017):160-77. \url{https://doi.org/10.5406/jsporthistory.44.2.0160}

\subsection{Digital History Projects}
Amanda Regan and Eric Gonzaba, \emph{Mapping the Gay Guides}, (in progress 2019-): \url{http://www.mappingthegayguides.org}.

Joshua Catalano and Amanda Regan, ``Mining Eleanor Roosevelt's \emph{My Day} Columns,'' (2017) \url{https://regan008.shinyapps.io/mining_my_day/}.

Jannelle Legg, Amanda Regan, and Anne Ladyem McDivitt, \emph{Roy Rosenzweig Center for History and New Media 20th Anniversary Archive}, (2014). \url{http://20.rrchnm.org/}.

\subsection{Conferences and Presentations}

``Mapping in the Humanities'' Civic Engagement & Voting Rights Teacher Scholars program, Clemson University, Clemson, SC, June 5, 2024.

``Building your Academic Network via Social Media and Networking,'' North American Society for Sport History Conference, Denver, CO, May 24, 2024.

``Getting Your First Website Up and Running,'' North American Society for Sport History Conference, Denver, CO, May 24, 2024.

``Mapping the Margins: Gay Travel Guides and the Promise of Digital History,'' Villanova University Digital Seed Series, April 18, 2024.

```Uncle Sam Wants You to Be Fit': Fitness, Civilian Defense, and War Work on the American Homefront, 1941-45,'' American Historical Association, San Francisco, CA January 6, 2024.

``\emph{Mapping the Gay Guides}: Using Digital Historical Methods to Explore LGBTQ Travel Guides,'' RCID Research Forum, Clemson University, November 13, 2023.

``\emph{Mapping the Gay Guides},'' GIS Day, Clemson Center for Geospatial Technologies, Clemson University, November 2023. 

Chair and moderator for ``Constructing Bodies: Women, Establishments, and Expectations of Femininity,'' Berkshire Conference of Women Historians, Santa Clara University, Santa Clara, CA, June 30, 2023.

``Building and Managing Datasets for Digital Public History Projects with Airtable,'' Digital Public History Lab at the National Council on Public History Annual Meeting, Atlanta, GA, April 2023. 

``Digital Methods for Understanding Historical Travel Guides: A Case Study of the Methodologies behind \emph{Mapping the Gay Guides},'' L. Dennis Shapiro and Susan R. Shapiro Digital History Seminar, Massachusetts Historical Society, February 2023. 

``Geography, Media, and Queer Community Formation,'' Panelist, Critical Digital Humanities International Conference, September 2022.

``Mapping Historical LGBTQ Locations with Mapping the Gay Guides,'' Mapping and Data for Social Justice, Clemson Center for Geospatial Technologies, September 2022.

``Acquiring Fitness: Using Temporal Word Embeddings to Trace the Evolution of 'Fitness' in Physical Education Journals,'' Physical Cultures of the Body 2022, H.J. Lutcher Stark Center at the University of Texas Austin, January 2022.

``Mapping the Gay Guides: Using Digital History to Understand Queer Spaces in America,'' Association for Computing in the Humanities Conference, July 2021.

``Mapping the Gay Guides: Using Digital History to Explore LGBTQ Travel Guides, 1965-1980,'' with Eric Gonzaba, Southern Methodist Univeristy, November 2020.

``Shaping the `Soft American`': The Presidential Council on Physical Fitness 1955-1963,'' Tasting Freedom at George W. Bush Presidential Library and Museum, April 2021.

``Mapping the Gay Guides: Understanding Queer Spaces in Pre- and Post-Stonewall America'', with Eric Gonzaba, DH2020, July 2020. \emph{[Cancelled due to COVID-19.]}

``Awash in a Sea of Content? Keep Up with the Field Using PressForward,'' with Joshua Catalano and Laura Crossley, Keystone DH, The Pennsylvania State University, July 2018.

``Mining Mind and Body: Approaches and Considerations for Using Topic Modeling to Identify Discourses in Digitized Publications,'' Doing Sport History in the Digital Present Workshop, Georgia Tech University, May 2016.

``Using the PressForward Plugin to Create Publications and Build Research Communities,'' with Amanda Morton, Advancing Research Communities and Scholarship Conference, Philadelphia, April 2015.

``Teaching Graduate Students to Code,'' contributor to poster session with Dr. Lincoln Mullen, American Historical Association conference, New York, January 2015.

\subsection{Grants}
PI, ``Shaping Up: Physical Fitness Initiatives for Women, 1880-1965.'' Faculty Research Development Program grant from the College of Architecture, Arts and Humanities, Clemson University (2023-2024): \$2,500.

Co-Project Director, ``Mapping the Gay Guides: Understanding Historical LGBTQ Spaces through Gay Travel Guides.'' Humanities Collections and Reference Resources grant from the National Endowment for the Humanities (2021-2024): \$349,894.

Co-Primary Investigator, \emph{Mapping the Gay Guides.} Research, Scholarship, and Creative Activities Incentive grant from California State University, Fullerton (2019-2020): \$14,715.

\subsection{Reviews}\label{reviews}

Review of \emph{Governing Bodies: American Politics and the Shaping of the Modern Physique}, by Rachel Louise Moran, \emph{The Journal of Social History} 53, no. 3 (2019): 851-2. \url{https://doi.org/10.1093/jsh/shz006}.

Review of \emph{Body and Nation: The Global Realm of U.S. Body Politics in the Twentieth Century}, Emily S. Rosenberg and Shannon Fitzpatrick, ed., \emph{The Journal of Social History}, 49, no.2 (2015):455–456. \url{https://doi.org/10.1093/jsh/shv046}.

\subsection{Academic and Research Positions}

Producer; \emph{The Past, The Promise, The Presidency Podcast: Season 1 Race and the American Legacy}; Center for Presidential History, Southern Methodist University, 2020-2021. \url{https://www.pastpromisepresidency.com}

Software Development Manager; PressForward; Roy Rosenzweig Center for History and New Media, George Mason University, August 2016-2018. \url{http://www.pressforward.org}

Managing Editor; \emph{Digital Humanities Now}; Roy Rosenzweig Center for History and New Media, George Mason University, August 2016-2018. \url{http://www.digitalhumanitiesnow.org}

Digital History Fellowship; Roy Rosenzweig Center for History and New Media, George Mason University, August 2013-2015.

Producer; \emph{Digital Campus Podcast}; Roy Rosenzweig Center for History and New Media, George Mason University, August 2013-2015. \url{http://digitalcampus.tv/}

Digital and Institutional Review Board Consultant; \emph{War at Home and Abroad Digital: A Digital History Archive,} Department of History, California State University San Marcos, August 2012-January 2013, \url{http://www.csusmhistory.org/WAHA}.

\subsection{Teaching Experience}

\textbf{Clemson University}
\begin{itemize}
  \itemsep0em 
  \item History 1010: United States History to 1877
  \item History 1020: United States History 1877-Present
  \item History 3050: United States History, 1918-1945
  \item History 3180: U.S. Women's History
  \item History 3890: Creative Inquiry - Mapping the Gay Guides
  \item History 8510: Methods in Digital History II
  \item History 8550: Seminar in Digital History
  \item History 8850: Independent Study in U.S. Women's History
\end{itemize}
\textbf{Other Institutions}
\begin{itemize}
  \itemsep0em 
  \item History 390: The Digital Past, George Mason University, 2017-2019.
  \item History 121: U.S. History to 1865, North Virginia Community College, Summer 2018.
  \item History 101: World Civilization to 1500, Teaching Assistant, California State University San Marcos, Spring 2013.
\end{itemize}

\subsection{Guest Lectures}
``\emph{Mapping the Gay Guides}'' in HON 2030: Cultural Theory and Pop Culture, Clemson University, March 2024.

``Data Ethics, Privacy, and the Creation of \emph{Mapping the Gay Guides}'' in HIST 8540: Topics in Digital History - The Ethics and History of Computers, Clemson University, November 2023.

``\emph{Mapping the Gay Guides}'' in HON 1910: Streaming Popular Feminisms, Clemson University, November 2023.

"Creating Historical Data and Documenting Queer Spaces with \emph{Mapping the Gay Guides}" in HON 2030: Cultural Theory and Pop Culture, CLemson University, March 2023.

"Programming for Historians" in Hist 8500: Digital Methods for History I, Clemson University, December 2022.

"\emph{Mapping the Gay Guides}" in HON 1910: Streaming Popular Feminisms (Honors First year seminar program), Clemson University, November 2022. 

"Algorithmic Bias" in SOC 2010: Introduction to Sociology, Clemson University, April 2022.

"Data and Historical Sources: Building Mapping the Gay Guides" in Introduction to Museum Studies, York College of Pennsylvania, April 2021.

"Digital Public History" in Introduction to Public History, Clemson University, December 2020.

"Distant Reading in the Digital Humanities" in Introduction for Digital Humanities, Xavier University of Louisiana, October 2020.

"Doing Research in the Digital Age: Managing Your Personal Archive with Zotero and Tropy," Intro to Digital Humanities, Southern Methodist University, February 2020.

\subsection{Select Media Appearances and Interviews}
"Mapping the Gay Guides," \emph{Atlas Obscura Podcast}, July 24, 2023. \url{https://www.atlasobscura.com/articles/podcast-mapping-the-gay-guides}

"Are the Humanities Ready for Data Sharing?," Ithaka S+R, March 6, 2023. \url{https://sr.ithaka.org/publications/are-the-humanities-ready-for-data-sharing/}

"Preserving and empowering LGBTQ+ lives with maps," TomTom, August 25, 2022.

"These Maps Once Showed Where Being Gay Was Safe," \emph{Next City Podcast,} July 27, 2022.

"Mapping the Gay Guides," \emph{Augmented Humanity Podcast}, New Mexico Humanities Council, June 2022.

\subsection{Digital Humanities Workshops}
Text Analysis with Voyant Tools, Collections As Data: Hack-to-Learn, Library of Congress, Washington D.C., May 2017.

Text Analysis for Digital Humanists, invited workshop and talk, University of California, Riverside, California, November 2016.

Graffiti Houses: The Civil War from the Perspective of Individual Soldiers; An NEH Landmarks in American History and Culture Workshop for Teachers, Graduate Research Assistant, George Mason University, June and July 2016.

Getting Started with PressForward, The Alfred P. Sloan PressForward Institute, 2015.

DC History Grad Zotero Workshop, with Jannelle Legg, George Mason University, October 2015.

DH Bridge: Encouraging Computational Thinking and Digital Skills in the Humanities, Coach, Roy Rosenzweig Center for History and New Media, George Mason University, October 2014.

\subsection{Department, College, and University Service}\label{Department, College, and University Service}
Member, Environmental History Search Commitee, Department of History and Geography, Clemson University, 2023.

Member, Graduate Committee, Department of History and Geography, Clemson University, 2023-present.

Website Manager, Department of History and Geography, Clemson University, 2022-present.

Member, Associate Dean for Undergraduate and Graduate Studies Search Committee, College of Architecture, Arts, and Humanities. Clemson University. Spring 2022.

\subsection{Service to the Profession}\label{Other Professional and Community Service}

% Communications Officer, Association for Computing in the Humanities, (July 2024 - present)

Deputy Communications Officer, Association for Computing in the Humanities, April 2024 - July 2024.

Reviewer, American Council of Learned Societies, Spring 2024.

Reviewer, National Endowment for the Humanities, Fall 2021, Spring 2022, and Spring 2024.

Member, Advisory Board, PressForward, (2022 - present).

Reviewer, Advanced Research Consortium (ARC), Fall 2022. 

Member, Advisory Board, Social Science Research Council, Research Area Mapping Platform project (2020 - present).

Reviewer, Digital Humanities 2020 Conference, Alliance of Digital Humanities Organizations, December 2019.

Participant, Manuscript workshop for Gregory Brew, Center for Presidential History, Southern Methodist University, November 2019.

Participant, Manuscript workshop for Lizzie Ingelson, Center for Presidential History, Southern Methodist University, October 2019.

Mentor, Diversity Outreach High School Program, Southern Methodist University, 2019-2020.

Participant, 2019 Mason Core assessment in IT and Computing, George Mason University, Spring 2019.

\subsection{Historical Visualizations and Other Digital Work}\label{other-digital-work}
``Mapping Gymnasiums in Boston,'' Visualization. \url{http://amanda-regan.com/bostongymnasiums/}.

Website redesign, \emph{PressForward}, January 2018, \url{http://www.pressforward.org}.

Website redesign, \emph{Appalachian Trail Histories}, January 2016. \url{http://appalachiantrailhistory.org/}.

``Twenty Years of RRCHNM History,'' Network Visualization, With Ken Albers, Peter Jones, Lincoln Mullen, Patrick Murray-John, Allison O’Connor, Faolan Cheslack-Postava, and Jannelle Legg, Fall 2014. \url{http://amanda-regan.com/RRCHNM20/}.

Digital Design Consultant, \emph{Wearing Gay History: A Digital Archive of Historical LGBTQ T-Shirts}, July 2015. \url{http://www.wearinggayhistory.org}.

\subsection{Awards and Honors}
Honorable Mention, Garfinkel Prize in Digital Humanities for \emph{Mapping the Gay Guides}, 2020, Digital Humanities Caucus of the American Studies Association.

Emerging Open Scholarship Award for \emph{Mapping the Gay Guides}, 2021, Canadian Social Knowledge Institute.

Louise and Rudolf Fishel Graduate Fellowship, 2018, George Mason University, Fairfax, VA.

Joseph and Dorothy Censer Fellowship, 2016, George Mason University, Fairfax, VA.

Larry J. Hackman Research Residency, 2016, New York State Archives, Albany, NY.

Provost's Dissertation Completion Travel Grant, 2016, George Mason University, Fairfax, VA.

Passed Ph.D. Oral Comprehensive Exams with Distinction, George Mason University, Fairfax, VA.

Digital History Fellowship, 2013-2015, Roy Rosenzweig Center for History and New Media, George Mason University, Fairfax, VA.

Digital Humanities Summer Institute Tuition Scholarship 2014, 2015, University of Victoria, Victoria, B.C.

Distinguished Master's Thesis Award, 2013, California State University, San Marcos, Department of History, San Marcos CA.


\subsection{Languages and Digital Humanities Skills}
\begin{itemize}
  \itemsep0em 
  \item\textbf{Programming Languages:} R, PHP, JavaScript, Go, Python
  \item\textbf{Web Development Languages:} CSS, HTML
  \item\textbf{Visualizations:} Shiny, D3.js, Leaflet
  \item\textbf{Tools:} ArcGIS, CartoDB, GitHub, GoogleRefine, MALLET, QGIS
  \item\textbf{CMS:} Omeka, WordPress
\end{itemize}

\subsection{Professional Memberships}
\begin{itemize}
  \itemsep0em 
  \item{Organization of American Historians}
  \item{American Historical Association}
  \item{Association for Computing in the Humanities}
\end{itemize}

\end{document}
